### 2020-04-12 draft_ABP.tex
Updates from Overleaf

{\Large \bf  Binary geometries: Associahedra, Cyclohedra and Generalized Permutahedra}

@@

From
\[
\prod_{i\not\in I}x_i=\prod_J u_J^{|J|-|I\cap J|}
\quad\text{and}\quad
\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
=
\prod_{J\supset I}u_J^{2^{|J|-|I|-1}},
\]
then
\[
\prod_{i\not\in I}x_i\bigg/\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
=\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}\prod_{J\supset I} u_J^{|J|-|I|-2^{|J|-|I|-1}}.
\]
Since $|J|-|I|-2^{|J|-|I|-1}\leq 0$, it's natural to conjecture that
\begin{equation}
1-u_I=g(u)\prod_{J\not\supset I} u_J^{|J|-|I\cap J|},
\end{equation}
where $g$ is a polynomial.
The product $\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}$ has appeared in all known examples with right powers. It's clear that any compatible $u_J$ for $J\subset I$ doesn't appear in the product because $I\cap J=J$. Thus, the final conjecture is about the compatibility degree:
\[
(I||J)=|J|-|I\cap J|\text{ for $I\not\subset J$},\quad  (I||J)=0 \text{ for $I\subset J$}.
\]
It's not symmetric when $|I|\neq |J|$.

@@

the $u$ variables are 
\begin{align}
   &u_{1}=\frac{x_{1}x_{123}}{x_{12}x_{13}} \:, \quad  u_{2}=\frac{x_{2}x_{123}}{x_{12}x_{23}} \:,  \quad 
   u_{3}=\frac{x_{3}x_{134}x_{234}x_{123}}{x_{34}x_{13}x_{23}x_{1234}} \:, \quad 
   u_{4}=\frac{x_{4}}{x_{34}} \\
   &u_{12}=\frac{x_{12}}{x_{123}} \:, \quad u_{13}=\frac{x_{13}x_{1234}}{x_{134}x_{123}} \:,\quad 
   u_{23}=\frac{x_{23}x_{1234}}{x_{123}x_{234}} \:, \quad u_{34}=\frac{x_{34}x_{1234}}{x_{134}x_{234}} \\
   &u_{123}=\frac{x_{123}}{x_{1234}} \:, \quad u_{134}=\frac{x_{134}}{x_{1234}} \:, \quad 
   u_{234}=\frac{x_{234}}{x_{1234}}
\end{align}
The $u$ equations are
\begin{align}
   &1-u_{1}=u_{2}u_{3}u_{23}^{2}u_{34}u_{234}^{2} \:, \\
   &1-u_{2}=u_{1}u_{3}u_{13}^{2}u_{34}u_{134}^{2} \:, \\
   &1-u_{3}= u_{1}u_{2}u_{4}u_{12}^{2}(1+u_{3}u_{13}u_{23}u_{34}u_{123}u_{134}u_{234}) \:, \\
   &1-u_{4}=u_{3}u_{13}u_{23}u_{123}  \:, \\
   &1-u_{12} =u_{3}u_{13}u_{23}u_{34}u_{134}u_{234} \:, \\
   &1-u_{13} =u_{2}u_{4}u_{12}u_{23}u_{34}u_{234}^{2} \:, \\
   &1-u_{23}= u_{1}u_{4}u_{12}u_{13}u_{34}u_{134}^{2} \:, \\
   &1-u_{34}= u_{1}u_{2}u_{12}^{2}u_{13}u_{23}u_{123}^{2} \:, \\
   &1-u_{123}=u_{4}u_{34}u_{134}u_{234} \:, \\
   &1-u_{134}=u_{2}u_{12}u_{23}u_{123}u_{234} \:, \\
   &1-u_{234}=u_{1}u_{12}u_{13}u_{123}u_{134} \:, 
\end{align} 
\subsection{Permutahedron as a binary geometry}
In this section we shall try to argue that the permutahedron is a binary geometry. We shall first summarise the following facts about the permutahedron from our discussion in the earlier sections:
\begin{enumerate}
\item The $u$-variables for the permutahedron are: 
\bea
u_J &=& ~~\prod_{J \subset I} x_I^{(-1)^{|I|-|J|}} \nonumber \\
u^{'}_J &=& \prod_{{0 \in I}\atop{ \{0,\cdots,n\} - I \subset J}} x_I^{(-1)^{|I|-|J|+mod(n, 2)}} \nonumber
\eea
From above it is evident that $u^{'}_{I} = u_{\bar{I}} $ where $\bar{I}=[0,n]-I$ for all subsets $I$ that do not contain $0$. 
And the $2^{n+1}-2$ facets corresponding to proper subsets of $[0,n]$ correspond to the two copies of the $2^{n}-1$ non-empty subsets of $[1,n]$.

\item From the definition of the permutahedron as a Nestohedron we know that $I$ and $J$ are :

@@

@@

\item  Since, the permutahedron is permutation invariant in all $x_i$'s this should be reflected at the level of $u$'s and all $u_I$ and $u^{'}_{J}$ with the same $|I|$ and $|J| =n-|I|$ should have similar $u$-equations. We see that this is indeed the case :

@@

 $K$ are all sets compatible with $I$ excluding itself

  $s_J$ are positive integers. 
\end{enumerate}
We shall now try to argue ${\mathscr P_n}$ is binary. We proceed inductively by first noticing that 
\section{Configuration spaces with perfect $u$-equations from degenerating $A_n$ and $B_n$}
In this section we shall consider some degenerations of $A_n$ and $B_n$ and show that these form an infinite class of examples of binary geometries with perfect $u$-equations. To do this we shall use the fact that both $A_n$ and $B_n$ are generalised permutahedra and can be realised as a Minkowski sum of coordinate simplices.

>>>>

{\Large \bf  Binary geometries: Associahedra, Cyclohedra and (Generalized) Permutahedra}

@@

From
\[
\prod_{i\not\in I}x_i=\prod_J u_J^{|J|-|I\cap J|}
\quad\text{and}\quad
\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
=
\prod_{J\supsetneq I}u_J^{2^{|J|-|I|-1}},
\]
then
\[
\prod_{i\not\in I}x_i\bigg/\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
=\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}\prod_{J\supsetneq I} u_J^{|J|-|I|-2^{|J|-|I|-1}}.
\]
Since $|J|-|I|-2^{|J|-|I|-1}\leq 0$, it's natural to conjecture that
\begin{equation}
1-u_I=g(u)\prod_{J\not\supset I} u_J^{|J|-|I\cap J|},
\end{equation}
where $g$ is a polynomial.
The product $\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}$ has appeared in all known examples with right powers. It's clear that any compatible $u_J$ for $J\subset I$ doesn't appear in the product because $I\cap J=J$. Thus, the final conjecture is about the compatibility degree:
\[
(I||J)=|J|-|I\cap J|\text{ for $I\not\subset J$},\quad  (I||J)=0 \text{ for $I\subset J$}.
\]
It's not symmetric when $|I|\neq |J|$.

@@

the $u$ variables are 
\begin{align}
   &u_{1}=\frac{x_{1}x_{123}}{x_{12}x_{13}} \:, \quad  u_{2}=\frac{x_{2}x_{123}}{x_{12}x_{23}} \:,  \quad 
   u_{3}=\frac{x_{3}x_{134}x_{234}x_{123}}{x_{34}x_{13}x_{23}x_{1234}} \:, \quad 
   u_{4}=\frac{x_{4}}{x_{34}} \\
   &u_{12}=\frac{x_{12}}{x_{123}} \:, \quad u_{13}=\frac{x_{13}x_{1234}}{x_{134}x_{123}} \:,\quad 
   u_{23}=\frac{x_{23}x_{1234}}{x_{123}x_{234}} \:, \quad u_{34}=\frac{x_{34}x_{1234}}{x_{134}x_{234}} \\
   &u_{123}=\frac{x_{123}}{x_{1234}} \:, \quad u_{134}=\frac{x_{134}}{x_{1234}} \:, \quad 
   u_{234}=\frac{x_{234}}{x_{1234}}
\end{align}
The $u$ equations are
\begin{align}
   &1-u_{1}=u_{2}u_{3}u_{23}^{2}u_{34}u_{234}^{2} \:, \\
   &1-u_{2}=u_{1}u_{3}u_{13}^{2}u_{34}u_{134}^{2} \:, \\
   &1-u_{3}= u_{1}u_{2}u_{4}u_{12}^{2}(1+u_{3}u_{13}u_{23}u_{34}u_{123}u_{134}u_{234}) \:, \\
   &1-u_{4}=u_{3}u_{13}u_{23}u_{123}  \:, \\
   &1-u_{12} =u_{3}u_{13}u_{23}u_{34}u_{134}u_{234} \:, \\
   &1-u_{13} =u_{2}u_{4}u_{12}u_{23}u_{34}u_{234}^{2} \:, \\
   &1-u_{23}= u_{1}u_{4}u_{12}u_{13}u_{34}u_{134}^{2} \:, \\
   &1-u_{34}= u_{1}u_{2}u_{12}^{2}u_{13}u_{23}u_{123}^{2} \:, \\
   &1-u_{123}=u_{4}u_{34}u_{134}u_{234} \:, \\
   &1-u_{134}=u_{2}u_{12}u_{23}u_{123}u_{234} \:, \\
   &1-u_{234}=u_{1}u_{12}u_{13}u_{123}u_{134} \:, 
\end{align} 
\subsection{Permutahedron as a binary geometry}

\textcolor{red}{(Prashanth: An attempt to prove $P_n$ is binary using Chi's method.)}

In this section we shall try to argue that the permutahedron is a binary geometry. We shall first summarise the following facts about the permutahedron:
\begin{enumerate}
\item The $u$-variables for the permutahedron are: 
\bea
u_J &=& ~~\prod_{J \subset I} x_I^{(-1)^{|I|-|J|}} \nonumber 
\eea
The above relations can also be inverted to obtain $x_I$ as follows:

For $0 \notin I $
\bea
x_I &=& \frac{\prod_{I \subset J} u_{J}}{1-\prod_{I \subset J} u_{J}} \\
\frac{1}{1+ x_I} &=& \prod_{{J}\atop{J\cap \bar{I} \ne \emptyset}} u_{\bar{J}}
\eea
From the above relations it is clear that taking $u_I \rightarrow 0$ for $0 \notin I$ implies $x_J \rightarrow 0$ for all $J \subset I$ and taking $u_\bar{I} \rightarrow 0$ for $0 \in I$ implies $x_J \rightarrow \infty $ for all $I \subset J$.
In fact we shall argue that there is unique choice of $x_I$'s which we can take to $0$ or $\infty$ which corresponds to setting a particular $u_I \rightarrow 0$ or $u_\bar{I} \rightarrow 0$ respectively.
\item From the definition of the permutahedron as a Nestohedron we know that $I$ and $J$ are :

@@

The above  follows directly from the following relations amongst $u$ for each $I$ such that $0\notin I$ :
\bea
1-\prod_{I \subset J} u_{J} &=& \prod_{{J}\atop{J\cap \bar{I} \ne \emptyset}} u_{\bar{J}} \\
1-\prod_{J \subset I} u_{\bar{J}} &=& \prod_{I \subset J} u_{J} \prod_{J \subset \bar{I} } u_{\bar{J}}
\eea

@@

\item  Since, the permutahedron is permutation invariant in all $x_i$'s this should be reflected at the level of $u$'s and this is indeed the case as $u_I$ with the same $|I|$ have similar $u$'s. i.e $u_J$ can be obtained from $u_I$ for $|J|=|I|$ by interchange of some of the $x_i$'s.

We shall prove $\mathscr P_{n+1}$ is binary by showing that whenever we take some $u_I \rightarrow 0$ (by taking a unique set of $x_i \rightarrow 0, \infty$) then $u_J \rightarrow 1$ for $J$ incompatible with $I$ and the remaining $u$'s reduce to the $u$'s corresponding to $\matchscr P_k \times \mathscr P_{n-k}$.

It is enough to consider $u_1, u_{12},\cdots,u_{12...n(n+1)} \rightarrow 0$ and  $u_0, u_{0(n+1)},u_{0,n(n+1)}\cdots,u_{02...n(n+1)} \rightarrow 0$.

We have the following cases:
\begin{enumerate}
    \item $u_I \rightarrow 0$ with $0\notin I$ and $|I| < \lfloor \frac{n+1}{2} \rfloor$ i.e $I = \{ \{1\},\{1,2\},\cdots,\{1,2,\cdots, \lfloor \frac{n+1}{2} \rfloor -1 \} \}$

    In this case we take $x_i \rightarrow t x_i$ for $i=1,\cdots \lfloor \frac{n+1}{2} \rfloor$ and consider the limit $t \rightarrow 0$ to give:
    \bea
    u^{(n+1)}_{J \cup  I} &\rightarrow& u_{J}^{((n+1)-|I|)} ~\text{with}~ J\subseteq\bar{I}\\
     u^{(n+1)}_{K} &\rightarrow& u_{K}^{(|I|-1)} ~\text{with}~ K\subsetneq I
    \eea
   which gives $\mathscr P_{(n+1)-|I|} \times \mathscr P_{|I|-1}$

    \item $u_I \rightarrow 0$ with $0\notin I$ and $|I| \ge \lfloor \frac{n+1}{2} \rfloor$ i.e. $I = \{\{1,2,\cdots, \lfloor \frac{n+1}{2} \rfloor\},\cdots,\{1,2,\cdots, (n+1) \} \}$
     In this case we take $x_i \rightarrow t x_i$ for $i=1,\cdots \lfloor \frac{n+1}{2} \rfloor-1$ and $x_{\lfloor \frac{n+1}{2} \rfloor} \rightarrow t$ and  consider the limit $t \rightarrow 0$ to give:
    \bea
    u^{(n+1)}_{J } &\rightarrow& u_{J}^{((n+1)-|I|)} ~\text{with}~ J\subseteq \{1,\cdots,|I|-1\}\\
     u^{(n+1)}_{J \cup \{|I|\}} &\rightarrow& u_{K \cup\{0\}}^{((n+1)-|I|)} ~\text{with}~ J\subsetneq I\{1,\cdots,|I|-1\}
    \eea
     \bea
    u^{(n+1)}_{K \cup I } &\rightarrow& u_{J}^{(|I|-1)} ~\text{with}~ K\subseteq \{|I|+1,\cdots,n+1\}\\
     u^{(n+1)}_{K \cup \{0\}\cup I} &\rightarrow& u_{K \cup{0}}^{(|I|-1)} ~\text{with}~ K\subsetneq I\{|I|+1,\cdots,n+1\}
    \eea
   which gives $\mathscr P_{(n+1)-|I|} \times \mathscr P_{|I|-1}$ 
    \item $u_I \rightarrow 0$ with $0\in I$ and $|I| < \lfloor \frac{n+1}{2} \rfloor$ i.e. $I = \{\{0\},\{0,(n+1)\},\cdots,\{0,\lfloor \frac{n+1}{2} \rfloor+2,\cdots,(n+1)\}$
    In this case we take $x_i \rightarrow \frac{ x_i}{t}$ for $i=1,\cdots \lfloor \frac{n+1}{2} \rfloor$ and $x_{\lfloor \frac{n+1}{2}+1 \rfloor} \rightarrow \frac{1}{t}$ and  consider the limit $t \rightarrow 0$ to give:
    \item $u_I \rightarrow 0$ with $0\in I$ and $|I| \ge \lfloor \frac{n+1}{2} \rfloor$ i.e. $I = \{\{0,\lfloor \frac{n+1}{2} \rfloor+1,\cdots,(n+1)\},\cdots,\{0,2,\cdots,(n+1)\} \}$
    In this case we take $x_i \rightarrow \frac{ x_i}{t}$ for $i=1,\cdots \lfloor \frac{n+1}{2} \rfloor$ and $x_{\lfloor \frac{n+1}{2}+1 \rfloor} \rightarrow \frac{1}{t}$ and  consider the limit $t \rightarrow 0$ to give:
\end{enumerate}

@@

 $K$ are all sets compatible with $I$ excluding itself 
 $s_J$ are positive integers.

\end{enumerate}
We shall now try to argue ${\mathscr P_n}$ is binary. We proceed inductively by first noticing that 
\section{Configuration spaces with perfect $u$-equations from degenerating $A_n$ and $B_n$}
In this section we shall consider some degenerations of $A_n$ and $B_n$ and show that these form an infinite class of examples of binary geometries with perfect $u$-equations. To do this we shall use the fact that both $A_n$ and $B_n$ are generalised permutahedra and can be realised as a Minkowski sum of coordinate simplices.
